Blocking-resistant communication\\through domain fronting

### 2015-02-11 docs/fronting.tex
Coax the survey table into \linewidth.

\begin{table*}[ht]
\centering
\begin{threeparttable}

\caption{
Summary of fronting-capable services.
Does not include some general classes of services (such as shared web hosting)
that may work for domain fronting.
Pricing is accurate as of February~2015.
A ``no'' in the ``allows SNI$\ne$Host'' means that the service requires the ``domainless'' fronting style.
}
\label{tab:survey}

\begin{tabular}{l r r r r c}
service                    &        \$/GB & \$/10K requests & \$/hour & \$/month & allows SNI$\ne$Host \\
\hline
Google App Engine\tnote{1} &        0.120 &              -- &    0.05 &       -- & yes \\
Amazon CloudFront          & 0.085--0.250 &    0.010--0.022 &      -- &       -- & yes \\
Microsoft Azure            & 0.087--0.138 &              -- &      -- &       -- & yes \\
CloudFlare                 &           -- &              -- &      -- &      200 & yes \\
Fastly\tnote{2}            & 0.120--0.190 &    0.010--0.012 &      -- &       -- & no  \\
Akamai\tnote{3}            &           -- &              -- &      -- &      400 & yes \\
Level~3\tnote{4}           & 0.035--0.200 &              -- &      -- &       -- & no  \\
% EdgeCast
\noalign{\smallskip}
\end{tabular}

\begin{tablenotes}
\item[1] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
\item[2] Fastly has a minimum monthly charge of \$50.
\item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB beyond that.
\item[4] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose. Level~3 does not publish pricing information; the prices here are from a reseller called VPS.NET, which quotes \$34.95 for the first 1000~GB and \$200 thereafter.
\end{tablenotes}

\end{threeparttable}
\end{table*}

>>>>

\begin{table}
\centering
\begin{threeparttable}

\caption{
Summary of fronting-capable services.
Does not include some general classes of services (such as shared web hosting)
that may work for domain fronting.
Prices are current as of February~2015 and are
rounded to the nearest cent.
}
\label{tab:survey}

\begin{tabular*}{\linewidth}{l r r r r}
service             &        \$/GB & \$/10K reqs. & \$/hour & \$/month \\
\hline
App Engine\tnote{1} &       0.12 &              -- &    0.05 &       -- \\
CloudFront          & 0.09--0.25 &      0.01--0.02 &      -- &       -- \\
Azure               & 0.09--0.14 &              -- &      -- &       -- \\
CloudFlare          &         -- &              -- &      -- &      200 \\
Fastly\tnote{2}     & 0.12--0.19 &            0.01 &      -- &       -- \\
Akamai\tnote{3}     &         -- &              -- &      -- &      400 \\
Level~3\tnote{4}    & 0.03--0.20 &              -- &      -- &       -- \\
% EdgeCast
\noalign{\smallskip}
\end{tabular*}

\begin{tablenotes}
\item[1] App Engine dynamically scales the number of ``instances'' of the application code in order to handle changing load. Roughly, every instance after the first costs \$0.05/hour.
\item[2] Fastly edge servers require that the SNI match the Host header, therefore it is necessary to use ``domainless'' fronting and omit SNI. There is a minimum monthly charge of \$50.
\item[3] Akamai does not publish pricing information; the prices here are from a reseller called Cache Simple, which quotes \$400/month for 1000~GB transfer, and \$0.50/GB for overages.
\item[4] Level~3 does support domain fronting per se, but paths under the \urll{secure.footprint.net} domain can likely serve the same purpose. Level~3 does not publish pricing information; the prices here are from a reseller called VPS.NET, which quotes \$34.95 for the first 1000~GB and \$200 thereafter.
\end{tablenotes}

\end{threeparttable}
\end{table}
